### 2015-09-10 vmcai-2016-tex/approach.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

The initialization rule in \figref{fig:symInit} is invoked whenever 
an uninitialized field is accessed. The interaction
with the solver in the definition of the rules is denoted by
$\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable.  The
check for uninitialized references is determined by the function
$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location
pairs where the field $\cfgnt{f}$ is uninitialized.
\[
\begin{array}{rcl}
\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\ & &
 \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\ & &
 \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
\end{array}
\]

@@

For a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the value set function computes 
the set of locations that the field could dereference to, paired with a local and valid access path constraint
that is feasible under the current path condition $\phi_g$.
The access path constraint is the union of two local constraints: 
the constraint $\phi$ from dereferencing $\cfgnt{r}$ to location $\cfgnt{l}$, 
and the constraint $\phi^\prime$ from dereferencing the field $\cfgnt{f}$ of the location $\cfgnt{l}$ to the actual location of the field, $\cfgnt{l}^\prime$. 
This access path constraint, paired with location $\cfgnt{l}^\prime$, is a member of the value set only if its union with the path condition is satisfiable, ensuring that the access path is valid and feasible under the path condition.
 % \nsr{neha: this para needs work -- flow and content tao: worked on the flow}

For field-write in~\figref{fig:fHeap}, after the non-null check and
strengthening of the global heap constraint, it computes the current
references associated with the field in every location in
$\Psi_\cfgnt{x}$. Note that the reference $\cfgnt{r}_x$ is the base
reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written to,
while the reference $r$ is the target reference. The set $\Psi_x$
contains tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints,
locations, and references. These tuples represent access chains
leading from $\cfgnt{r}_x$ to the reference of the field,
$\cfgnt{r}_\mathit{cur}$. The goal is to change the fields to no
longer point to $\cfgnt{r}_\mathit{cur}$, but rather fresh references
that have both the original locations before the write and the
locations from the write in the value sets (i.e., conditional
write). Since the target of the write is $r$, the rule checks that the
location constraint pairs of $\cfgnt{L}(\cfgnt{r})$ are satisfiable
when accessed through the $\cfgnt{r}_x$ chain in the strengthening
function.  \input{st-def} Constraints on locations are strengthened
with new aliasing conditions and those that are feasible with the
current path condition are retained.

Strengthening in the field write creates a value set that contains two
types of locations: those for the case where the write is feasible
(the first call), and those for the case where it is not (the second
call). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
will point to the constraint location pairs of $\cfgnt{L}(\cfgnt{r})$.
Whereas, if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will
continue to point to the constraint location pair it currently
references.  As the references are immutable, the rule creates fresh
references for each $\cfgnt{r}_\mathit{cur}$ and points them to the
appropriate value sets.

@@

Consider the example in~\figref{fig:initHeap}(c). In order to to check
if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
pairs associated with each of the references:
\[
\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
\]
\[
\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
\]
\noindent{The three constraint sets are:} 
\[
\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
\]
\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
\]

>>>>

The initialization rule in \figref{fig:symInit} is invoked whenever 
an uninitialized field is accessed. The interaction
with the solver in the definition of the rules is denoted by
$\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable.  The
check for uninitialized references is determined by the function
$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which a returns guarded value set 
containing those locations where the field $\cfgnt{f}$ is uninitialized.
\[
\begin{array}{rcl}
\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\ & &
 \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\ & &
 \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
\end{array}
\]

@@

For a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the value set function computes 
the guarded value set of locations and access path constraints
that are feasible under the current path condition $\phi_g$.
The access path constraint is the union of two local constraints: 
the constraint $\phi$ from dereferencing $\cfgnt{r}$ to location $\cfgnt{l}$, 
and the constraint $\phi^\prime$ from dereferencing the field $\cfgnt{f}$ of the location $\cfgnt{l}$ to the actual location of the field, $\cfgnt{l}^\prime$. 
This access path constraint, paired with location $\cfgnt{l}^\prime$, is a member of the value set only if its union with the path condition is satisfiable, ensuring that the access path is valid and feasible under the path condition.
 % \nsr{neha: this para needs work -- flow and content tao: worked on the flow}

For field-write in~\figref{fig:fHeap}, after the non-null check and
strengthening of the global heap constraint, it computes the current
references associated with the field in every location in
$\Psi_\cfgnt{x}$. Note that the reference $\cfgnt{r}_x$ is the base
reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written to,
while the reference $r$ is the target reference. The set $\Psi_x$
contains tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints,
locations, and references. These tuples represent access chains
leading from $\cfgnt{r}_x$ to the reference of the field,
$\cfgnt{r}_\mathit{cur}$. The goal is to change the fields to no
longer point to $\cfgnt{r}_\mathit{cur}$, but rather fresh references
that have both the original locations before the write and the
locations from the write in the value sets (i.e., conditional
write). Since the target of the write is $r$, the rule checks that the
constraints of the guarded value set $\cfgnt{L}(\cfgnt{r})$ are satisfiable
when accessed through the $\cfgnt{r}_x$ chain in the strengthening
function.  \input{st-def} Constraints on locations are strengthened
with new aliasing conditions and those that are feasible with the
current path condition are retained.

Strengthening in the field write creates a value set that contains two
types of locations: those for the case where the write is feasible
(the first call), and those for the case where it is not (the second
call). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
will point to the guarded value set $\cfgnt{L}(\cfgnt{r})$.
Whereas, if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will
continue to point to the constraint location pair it currently
references.  As the references are immutable, the rule creates fresh
references for each $\cfgnt{r}_\mathit{cur}$ and points them to the
appropriate value sets.

@@

Consider the example in~\figref{fig:initHeap}(c). In order to to check
if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the 
guarded value set associated with each of the references:
\[
\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
\]
\[
\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
\]
\noindent{The three constraint sets are:} 
\[
\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
\]
\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
\]

### 2015-09-10 vmcai-2016-tex/evaluation.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

To resolve this question, we implemented a prototype of the \symtxt{} 
algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
and evaluate its efficacy on three Java data structure artifacts.
%SPF includes an implementation of~\gsetxt{} with lazy initialization.
%In recent work, we implemented the  Lazier and Lazier\#
%algorithms in SPF~\cite{Hillery:2014}.
%
%The prototype of our~\symtxt{} algorithm is implemented as an
%extension to SPF.  
In addition to the operations presented in
this paper, the implementation contains support for operations over
integers, calculating per-path preconditions 
and postconditions, as well as path-coverage-optimal sets of 
test input heaps. 
%A standalone version of the system, independent
%from JPF is also under development~\cite{heapsolver2015}.

The benchmarks focus on a number of common data structures, including a linked list, binary search tree, and red/black tree. The BinarySearchTree test uses the class of the same name from Alan Weiss' book titled ``Data Structures and Algorithm Analysis in Java''. The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree. The TreeMap method comes from the standard java.util library, and is an implementation of a balanced red/black tree. This method asserts a repOk() invariant, before traversing the tree. The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm. The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list. For benchmarking purposes, the length of reference chain initializations was limited to some integer $k$. More details on $k$-bounding can be found in~\cite{Deng:2007}.

@@

The results demonstrate that for these common data structures,
the complexity of the constraints generated by~\symtxt{} is more 
than offset by the reduction in paths explored. Performance improvement ranges from $4.8x$ for
BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
for some $k$-bounds a number of experiments completed exploration
using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
$k$=8. However, these numbers should 
not be taken as an indication of performance gains that could be 
expected in more general analysis situations. Real-world performance
gain will most likely depend on the proportion of paths avoided that
would otherwise have been explored via case-splitting.

>>>>

To resolve this question, we implemented a prototype of the \symtxt{} 
algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
and evaluate its efficacy on Java data structure artifacts.
%SPF includes an implementation of~\gsetxt{} with lazy initialization.
%In recent work, we implemented the  Lazier and Lazier\#
%algorithms in SPF~\cite{Hillery:2014}.
%
%The prototype of our~\symtxt{} algorithm is implemented as an
%extension to SPF.  
In addition to the operations presented in
this paper, the implementation contains support for operations over
integers, calculating per-path preconditions 
and postconditions, as well as path-coverage-optimal sets of 
test input heaps. 
%A standalone version of the system, independent
%from JPF is also under development~\cite{heapsolver2015}.

The data structures used in the benchmarks are a standard set commonly used in analyses involving heap-manipulating programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015}, including a linked list, binary search tree, and red/black tree. The BinarySearchTree test uses the class of the same name from Alan Weiss' book~\cite{Weiss:1998}. The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree. The TreeMap method comes from the standard java.util library, and is an implementation of a balanced red/black tree. This method asserts a repOk() invariant, before traversing the tree. The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm. The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list. For benchmarking purposes, the length of reference chain initializations was limited to some integer $k$. For both the tree examples, the number of possible non-isomorphic tree structures grows exponentially in k~\cite{Deng:2007}, resulting a corresponding exponential growth in analysis times for case-splitting techniques.

@@

Performance improvement ranges from $4.8x$ for
BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
for some $k$-bounds a number of experiments completed exploration
using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
$k$=8. The results demonstrate that for these common data structures,
the complexity of the constraints generated by~\symtxt{} is more 
than offset by the reduction in paths explored.

### 2015-09-10 vmcai-2016-tex/intro.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

The contribution of this work is to build on previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, and by proving that the dereferencing scheme is sound and complete with respect to properties provable by symbolic execution. A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to existing case-splitting methods.

>>>>

The contribution of this work is to build on previous efforts, by demonstrating an initialization scheme that enables pointer dereferencing in an unknown symbolic input heap, and by proving that the initialization scheme is sound and complete with respect to properties provable by symbolic execution. A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to existing case-splitting methods.

### 2015-09-10 vmcai-2016-tex/lazy.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

>>>>

The~\gsetxt{} initialization rules preserve several important properties of the symbolic heap. In the heap generated by~\gsetst{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals}.
  Only input heap references appear in constraints to express potential aliasing.
  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations. Changes to $R$ are monotonically increasing, eliminating any need for constraint rewriting as the program state evolves.
A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

### 2015-09-10 vmcai-2016-tex/summary-heap.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

A \emph{symbolic heap} is a tuple $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map} $\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment} $\eta$ are partial functions, and the~\emph{path condition} $\phi$ is a predicate over the program variables. Given reference $r$, $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs (guarded value set) in the heap associated with $r$. The constraint  associated with each location is a guard
representing the conditions under which the associated reference
maps to the given location. By definition, any location appears 
at most once in any given value set. Unions of value sets containing
the same location are resolved by forming a disjunction of the constraints
from each set. $\cfgnt{R}(\cfgnt{l}, \cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap. The environment  $\eta$ maps local variables to references.

@@

Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the initial machine state is
$$
\begin{array}{l}
\lp\mu 
\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
\ \cfgnt{R}
\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
\end{array}
$$
The expression in the initial state constructs a new object of type
$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
object.

The semantics are expressed as
rewrites on strings using pattern matching. 
%Consider the rewrite rule
%for the beginning of a field access instruction:
%$$
%\mprset{flushleft}
%	\inferrule[Field Access(eval)]{}{
%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
%	}
%$$
%If the string representing the current state matches the left side, then it
%creates the new string on the right. In this example, the new string
%on the right is now evaluating the expression $\cfgnt{e}$ in the field
%access, and it includes the continuation indicating that it still
%needs to complete the actual field access once the expression is
%evaluated.
%
%Other more complex rules, such as one to create a new instance of a
%class, define constraints on the rewrites and more complex
%transformations on the heap.
%$$
%\mprset{flushleft}
%	\inferrule[New]{
%      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
%      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
%      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
%      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
%    }{
%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
%      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
%	}
%$$ In this rule, when the string matches the new-expression, it is
%        rewritten to use a new heap location where all of the fields
%        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
%        location map points a new stack reference to that new object.
%        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
%        increasing.
%        Also note that references for objects from the new-expression are
%        auxiliary literals, so they do not appear in any constraint in
%        the symbolic heap as an aliasing option. 
%        
% \input{javalite-common}
%
The rewrite relations for the portion of the language
semantics that are common to both generalized symbolic execution and
the symbolic heap algorithm may be found in \cite{Hillery:2015}. The relation $\rcom$ includes all of these
rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking or error conditions. The
machine simply halts if no rewrite is enabled.

@@

\subsection{Symbolic Heap}

@@

Certain characteristics of the symbolic heap are preserved by
the small-step semantics during symbolic execution:

\begin{compactdesc}
\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals}. %(these appear in environments, expressions, and continuations).
  Only input heap references appear in constraints to express potential aliasing.
  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
\item[Null and Uninitialized:] Every symbolic heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
\item[Immutability:] References do not change once added to the
location map, eliminating any need for constraint rewriting as the program state evolves.
\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
\item[Type consistency:] All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

\end{compactdesc}

>>>>

A \emph{symbolic heap} is a tuple $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map} $\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment} $\eta$ are partial functions, and the~\emph{path condition} $\phi$ is a predicate over the program variables. Given reference $r$, $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set in the heap associated with $r$. The constraint  associated with each location is a guard
representing the conditions under which the associated reference
maps to the given location. By definition, any location appears 
at most once in any given value set. Unions of value sets containing
the same location are resolved by forming a disjunction of the constraints
from each set. $\cfgnt{R}(\cfgnt{l}, \cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap. The environment  $\eta$ maps local variables to references.

@@

Execution begins with the initial machine state. The expression for the initial state constructs a new object of type
$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
object. The initial symbolic heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
$$
\begin{array}{l}
\lp\mu 
\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
\ \cfgnt{R}
\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
\end{array}
$$

The semantics are expressed as
rewrites on strings using pattern matching. 
Consider the rewrite rule
for the beginning of a field access instruction:
$$
\mprset{flushleft}
	\inferrule[Field Access(eval)]{}{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
	}
$$
If the string representing the current state matches the left side, then it
creates the new string on the right. In this example, the new string
on the right is now evaluating the expression $\cfgnt{e}$ in the field
access, and it includes the continuation indicating that it still
needs to complete the actual field access once the expression is
evaluated.
%
%Other more complex rules, such as one to create a new instance of a
%class, define constraints on the rewrites and more complex
%transformations on the heap.
%$$
%\mprset{flushleft}
%	\inferrule[New]{
%      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
%      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
%      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
%      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
%    }{
%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
%      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
%	}
%$$ In this rule, when the string matches the new-expression, it is
%        rewritten to use a new heap location where all of the fields
%        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
%        location map points a new stack reference to that new object.
%        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
%        increasing.
%        Also note that references for objects from the new-expression are
%        auxiliary literals, so they do not appear in any constraint in
%        the symbolic heap as an aliasing option. 
%        
% \input{javalite-common}
%

The rewrite relations for the portion of the language
semantics that are common to both generalized symbolic execution and
the symbolic heap algorithm may be found in \cite{Hillery:2015}. The relation $\rcom$ includes all of these
rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking or error conditions. The
machine simply halts if no rewrite is enabled.

@@

@@
